\mytitle

### 2021-12-09 paper.tex
adding references
extend intro

The development of modern CPUs with support for instruction\-/level
parallelism (ILP) opens the opportunity for a further reduction of the
runtime of the calculation of the dilogarithm, given an appropriate
formulation of the algorithm.  In this paper an algorithm for the
calculation of the real dilogarithm $\Li$ is presented, which makes
use of ILP, resulting in a reduced runtime compared to the algorithms
presented so far.  A C implementation of this algorithm can be found
in the appendix and in the arXiv submission of this paper.

@@

C, C++ and FORTRAN implementations of the presented algorithm can be
found in the Polylogarithm library \cite{polylogarithm}.

>>>>

The development of modern CPUs with support for instruction\-/level
parallelism (ILP) opens the opportunity for a further reduction of the
runtime of the calculation of the dilogarithm.  To make use of ILP,
the algorithm to calculate the dilogarithm must be formulated
appropriately in order to allow for the parallel execution of multiple
floating\-/point operations.  In this paper an algorithm for the
calculation of the real dilogarithm $\Li$ is presented, which makes
use of ILP, resulting in a reduced runtime compared to the algorithms
presented so far.  A C implementation of this algorithm can be found
in the appendix and in the arXiv submission of this paper.

@@

C, C++ and FORTRAN implementations of the presented algorithm can be
found in the Polylogarithm library \cite{polylogarithm}.
Implementations in Julia and Rust can be found in \cite{PolyLog.jl}
and \cite{polylog}, respectively.
